\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}
\usepackage{fontawesome}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc} % replace the encoding
\usepackage[scale=0.8]{geometry} % adjust page margins

% personal data
\name{Desmond}{Sylvester}
\title{Software Developer}
\address{No 12 McNeil Street, Sabo}{Yaba, Lagos}
\phone[mobile]{+234~(806)~749~0432}
\email{kukiito219@gmail.com}
\social[twitter]{meetKazuki}
\social[linkedin]{desmondedem}
\social[github]{meetKazuki}
\quote{Learn. Improve. Contribute...}

% content
\begin{document}

\makecvtitle

\section{Education}
\cventry{2017}{B.Sc. Computer Science}{University of Uyo}{Uyo}{}{}
\cventry{2009}{WASSCE}{Immaculate Conception Seminary}{Mfamosing}{}{}

\section{Work Experience}
\cventry{2018--}{Freelance 3D Modeller}{}{}{}{Learnt blender3D and worked on little projects for different clients. Main area of focus was using blender3D for architectural visualization.}
\cventry{2017--May. 2018}{Founder, Community Manager}{Club Sierra Gaming Community}{Calabar}{}{Founded this community with my friend John-Bosco Ihionu. A small PES gaming community with the aim of kickstarting eSports, growing IT literacy within our members, and pursuing other creative ventures in the State. I was responsible for hosting gaming events, and handling affairs on the social media front. Before I left, the community grew to about 20-man strong.}
\cventry{Feb--Dec. 2017}{Social Media Coordinator}{The Dialogue with Agba Jalingo}{Calabar}{}{Curated contents on all TDWAJ social media platforms. Handled live coverage of the quarterly townhall meetings on social media. Installing, configuring, and troubleshooting systems for the smooth running of the day-to-day TDWAJ activities.}
\cventry{2014--2015}{Intern}{Akwa Ibom State Ministry of Science \& Technology}{Uyo}{}{Assisted with installing, configuring, and troubleshooting different computer systems and other networking facilities within the Ministry.}

\section{Skills}
\subsection{Have Some Proficiency In}
\cvline{languages}{HTML5, CSS, JavaScript, \LaTeX{}}
\cvline{technologies}{Windows, Android, Ubuntu (WSL), Visual Studio Code, GitHub, Share\LaTeX{}, Slack, Discord, MS-Office (Word, Excel, PowerPoint, OneNote), blender3D, Cycles Render, Gimp, Inkscape}
\subsection{Have Some Experience With}
\cvline{languages}{C\#, C++, Python, BASIC, Lisp}
\cvline{technologies}{Visual Studio, wxWidgets, WordPress, urho3D, Bash Scripting, Cygwin, Photogrammetry, MeshLab, VisualSFM}
\subsection{Inter-Personal Skills}
\cvlistitem{Able to communitcate complex IT issues to non-technical staff.}
\cvlistitem{Ability to work well in a team environment.}
\cvlistitem{Attention to details.}
\cvlistitem{Fast learner and always open to criticism.}
\cvlistitem{Always itching for new ways of solving problems.}

\section{Conferences Attended}
\cventry{2017}{OpenCon 2017}{}{Calabar}{}{}
\cventry{2018}{The Bridge Leadership Foundation 8th Career Day}{}{Calabar}{}{}

\section{Certifications}
\cventry{November 2017}{OpenCon 2017}{Certificate of Attendance}{}{}{}
\cventry{May 2018}{Andela Learning Community (ALC) 2.0}{Web Beginner Development Bundle}{}{}{}

\section{Interests and Hobbies}
\cvline{Interests}{Stack Overflow \faStackOverflow, Open-Source Software, 3D Design \& CGI, Photography, The Dark Web}
\cvline{Hobbies}{Programming, Typesetting, Reading, Football, Video Games}

\section{References}
\textit{Available on request.}
% \cvlistitem{\textbf{Mr. Agba Jalingo}\newline\textit{Publisher-in-Chief},\newline{Cross River Watch, Calabar.}}
% \cvlistitem{\textbf{Mr. Evaristus Ekpenyong}\newline\textit{Project Manager,}\newline{Courteville Business Solutions}}

\end{document}