\documentclass[11pt, a4paper, sans]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage{color, graphicx}
\usepackage[scale=0.8]{geometry}              % Width of the entire CV
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{moderntimeline}
\usepackage{pdfpages}
\usepackage{xpatch}

\recomputelengths
\setlength{\hintscolumnwidth}{2cm}            % Width of the timeline on your left
\tlmaxdates{2018}{2030}                       % Beginning and start of your timeline

%  //////////////////////////////////////////////////////////////////////
%  ------------------------ Personal Information ------------------------
%  //////////////////////////////////////////////////////////////////////

\name{Desmond}{Edem}
\title{Backend Engineer}
\address{42 Cole Street}{Surulere, Lagos}
\phone[mobile]{+234~(806)~749~0432}
\social[linkedin]{desmondedem}
\social[github]{meetkazuki}
\email{meetdesmond.edem@gmail.com}
\extrainfo{https://meetkazuki.github.io}
\quote{Learn. Improve. Contribute\ldots}

\begin{document}

\makecvtitle

%  //////////////////////////////////////////////////////////////////////
%  -------------------------- Work Information --------------------------
%  //////////////////////////////////////////////////////////////////////

\section{Work Experience}

\tlcventry{2025}{0}{Lead Backend Engineer (Volunteer)}{African Institute for AI LBG}{Accra, Ghana}{}{
  \begin{itemize}
    \item Leading the development of a scalable backend architecture for an AI-driven platform, focusing on performance and reliability.
    \item Implementing best practices in API design and database management to support high traffic and data-intensive applications.
    \item Collaborating with cross-functional teams to integrate AI models and ensure seamless deployment of machine learning solutions.
  \end{itemize}
}

\medskip

\cvline{}{Tools: \textit{TypeScript, Node.js, PostgreSQL, Redis, Terraform, Azure, Docker, Retool.}}

\tlcventry{2021}{2024}{Backend Engineer}{STRV s.r.o}{Prague, Czech}{}{
  \begin{itemize}
    \item Led technical discovery and architecture design for 6+ MVP projects, translating client visions into scalable solutions with average time-to-market of 8 months.
    \item Designed and implemented cost-effective backend infrastructures for US-based startups, reducing initial cloud costs by up to 40\% while maintaining scalability.
    \item Architected database schemas and API structures that enabled seamless scaling from MVP to production, supporting 5x user growth without major refactoring.
    \item Progressed from collaborative development to independently leading technical discussions with clients and defining solution architectures.
    \item Established coding standards and review processes that reduced technical debt by 50\% and improved maintainability across client projects.
  \end{itemize}
}

\medskip

\cvline{}{Tools: \textit{TypeScript, Node.js, PostgreSQL, MongoDB, Redis, AWS Elastic Beanstalk, Heroku.}}

\medskip

\tlcventry{2020}{2021}{Backend Developer}{Pettysave Limited}{Lagos State, Nigeria}{}{
  \begin{itemize}
    \item Assisted in developing server-based Node.js software by providing inputs and insights.
    \item Improved peer review process by automating Pull Requests deployment and enhancing work collaboration between different stakeholders.
    \item Increased customer retention by 27\% by implementing email marketing automation across user journey, using Sendgrid.
    \item Collaborated together with the product and marketing team to implement product-led growth strategies like in-app reward systems, gamification and social features.
  \end{itemize}
}

\medskip

\cvline{}{Tools: \emph{JavaScript, Node.js, Adonis.js, GraphQL, MySQL, Heroku.}}

\medskip

\tlcventry{2020}{2020}{Fullstack Developer}{Nester Global Solution Services}{}{Lagos State, Nigeria}{
  \begin{itemize}
    \item Maintained, reviewed and developed the firm’s enterprise and web .
    \item Involved with application management and monitoring.
    \item Deployed solutions on Microsoft Azure and setting up cron jobs.
  \end{itemize}
}

\medskip

\cvline{}{Tools: \textit{JavaScript, Node.js, Vue.js, MongoDB, Microsoft Azure.}}

\medskip

\tlcventry{2019}{2019}{Backend Developer (Intern)}{DevCareers}{}{Lagos State, Nigeria}{Worked closely with a team of nine developers to build web applications for the organization. My responsibilities during this period was:
  \begin{itemize}
    \item Designed and configured a fully automated CI/CD lifecycle resulting in faster development time.
    \item Implementing API endpoints for the Frontend team to work with.
  \end{itemize}
}

\medskip

\cvline{}{Tools: \textit{JavaScript, Node.js, PostgreSQL, Heroku.}}

\medskip

\tlcventry{2018}{2019}{Software Developer (Intern)}{Andela Nigeria}{}{Lagos State, Nigeria}{I was part of an AGILE team composed of a Product Owner, Project Manager, Technical Team Lead and five engineers tasked with building REST API endpoints for a travel agency web application using NodeJS, Sequelize, and PostgreSQL.}

\medskip

\cvline{}{Tools: \textit{JavaScript, Node.js, HTML/CSS, PostgreSQL, Heroku.}}

%  //////////////////////////////////////////////////////////////////////
%  ------------------------ Skills Information --------------------------
%  //////////////////////////////////////////////////////////////////////

\section{Technical Skills}

\medskip

\cvitemwithcomment{Languages}{TypeScript, Python, \LaTeX, Ruby}{}

\cvitemwithcomment{Tools}{Docker, CI/CD, IaCs (AWS, Azure, GCP, Heroku), SQL Databases, NoSQL Databases}{}

\cvitemwithcomment{Architecture}{API Design (REST/GraphQL), Database Design, Event-Driven Systems, LLM Integrations}{}

%  //////////////////////////////////////////////////////////////////////
%  ------------------------ Miscellaneous Information --------------------------
%  //////////////////////////////////////////////////////////////////////

\section{Other Volunteer Experience}

\medskip

\tlcventry{2025}{0}{Backend Engineer}{African Institute for Artificial Intelligence LBG}{Accra, Ghana}{}{The African Association for the Advancement of Artificial Intelligence (4AI) is a visionary organization dedicated to advancing AI knowledge and application across Africa.}

\medskip

\tlcventry{2022}{2024}{Mentor}{DevCareer}{Lagos, Nigeria}{}{DevCareer is a Non-Profit organization that is focused on supporting upcoming developers with resources to excel into world class.}

\medskip

\tlcventry{2019}{2020}{Programming Tutor}{CodeLagos}{Lagos, Nigeria}{}{CodeLagos is an initiative of the Lagos State Ministry of Education aimed at making coding education accessible to Lagos State residents.}

\end{document}
